WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-04-16 ms.tex
Try to weave appendices into the paper better

@@

\section{Uncertainty and the Fisher matrix}
\label{sec:fisher}

We can predict the uncertainty in the \ac{ML} estimates without working out its full distribution. The \ac{CRLB} gives its covariance in the asymptotic limit of high \ac{SNR}. The \ac{CRLB} has been widely applied in \ac{GW} data analysis to estimate parameter estimation uncertainty (for example, \cite{1996PhRvD..53.3033B,FairhurstTriangulation,2009PhRvD..79h4032A,WenLocalizationAdvancedLIGO,LIGOObservingScenarios,FairhurstLIGOIndia})\footnote{The Fisher matrix is also used in construction of \ac{CBC} matched filter banks. The common procedure is to place templates uniformly according to the determinant of the signal space metric, which is the Fisher matrix. This is equivalent to uniformly sampling the Jeffreys prior. In practice, this is done either by constructing a hexagonal lattice \citep{PhysRevD.76.102004} or sampling stochastically \citep{2009PhRvD..80j4014H,2009PhRvD..80b4009V,SBank,2010PhRvD..81b4004M,2014PhRvD..89b4003P}}. We will momentarily consider the likelihood for a single detector:
%
\begin{multline}\label{eq:gaussian-likelihood-spa}
    \mathcal{L}\left(Y_i; \rho_i, \gamma_i, \tau_i,
        \bm\theta_\mathrm{in}\right)
    \\
    \propto \exp \left[
        - \frac{1}{2} \int_0^\infty \frac{\left|Y_i (\omega)
            - X_i\left(\omega; \rho_i, \gamma_i, \tau_i,
                \bm\theta_\mathrm{in}\right)
        \right|^2}{S_i(\omega)} \, d\omega
    \right],
\end{multline}
%
with $X_i(\omega; \rho_i, \gamma_i, \tau_i, \bm\theta_\mathrm{in})$ given by Equation~(\ref{eq:signal-model}).

The Fisher information matrix for a measurement $y$ described by the unknown parameter vector $\bm{\theta}$ is the conditional expectation value
%
\begin{equation}\label{eq:general-fisher-matrix}
    \mathcal{I}_{jk} = \mathrm{E} \, \left[
        \left(\frac{\partial \log
            \mathcal{L}(Y_i ; \bm\theta)}
            {\partial \theta_j}\right)
        \left(\frac{\partial \log
            \mathcal{L}(Y_i ; \bm\theta)}
            {\partial \theta_k}\right)
    \middle| \bm\theta
    \right].
\end{equation}
%
Note that if $\log\mathcal{L}$ is twice differentiable in terms of $\bm\theta$, then the Fisher matrix can also be written in terms of second derivatives as
%
\begin{equation}\label{eq:general-fisher-matrix-second-derivatives}
    \mathcal{I}_{jk} = \mathrm{E} \, \left[
        -\frac{\partial^2 \log
            \mathcal{L}(Y_i ; \bm\theta)}
            {\partial \theta_j \partial \theta_k}
    \middle| \bm\theta
    \right].
\end{equation}
%
In this form, we can recognize the Fisher matrix as the expectation value, conditioned upon the true parameter values, of the Hessian matrix of the log likelihood. It describes how strongly the likelihood depends, on average, on the parameters. If $\hat{\bm\theta}$ is an unbiased estimator of $\bm\theta$, $\tilde{\bm\theta} = \hat{\bm\theta} - \bm\theta$ is the measurement error, and $\Sigma = \mathrm{E} \, [\tilde{\bm\theta}\tilde{\bm\theta}\transpose]$ is the covariance of the measurement error, then the \ac{CRLB} says that $\Sigma \geq \mathcal{I}^{-1}$, in the sense that $\left(\Sigma - \mathcal{I}^{-1}\right)$ is positive semi\nobreakdashes-definite.

When (as in our assumptions) the likelihood is Gaussian, Equation~(\ref{eq:general-fisher-matrix}) simplifies to
%
\begin{equation}\label{eq:gaussian-fisher-matrix}
    \mathcal{I}_{jk} = \int_0^\infty \Re \left[
        \left(\frac{\partial X_i}{\partial \theta_j}\right)^*
        \left(\frac{\partial X_i}{\partial \theta_k}\right)
    \right] \frac{1}{S_i(\omega)} \, d\omega.
\end{equation}
%
This form is useful because it involves manipulating the signal $X_i (\omega)$ rather than the entire observation $Y (\omega)$. In terms of the $k$th \ac{SNR}-weighted moment of angular frequency,
%
\begin{equation}\label{eq:angular-frequency-moments}
    {\overline{\omega^k}}_i =
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \omega^k \, d\omega \right]
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \, d\omega \right]^{-1},
\end{equation}
%
the Fisher matrix for the signal in the $i$th detector is
%
\begin{equation}
    \mathcal{I}_i = \left(
        \begin{array}{cc}
            \mathcal{I}_{\bm\theta_i,\bm\theta_i} &
            \mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}} \\
            {\mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}}}\transpose &
            {\rho_i}^2 \mathcal{I}_{\bm\theta_\mathrm{in},\bm\theta_\mathrm{in}}
        \end{array}
    \right)
\end{equation}
%
where
%
\begin{equation}\label{eq:fisher-matrix}
    \mathcal{I}_{\bm\theta_i,\bm\theta_i} = \bordermatrix{
        ~ & \rho_i & \gamma_i & \tau_i \cr
        \rho_i & 1 & 0 & 0 \cr
        \gamma_i & 0 & {\rho_i}^2 & -{\rho_i}^2 {\overline{\omega}}_i \cr
        \tau_i & 0 & -{\rho_i}^2 {\overline{\omega}}_i & {\rho_i}^2 {\overline{\omega^2}}_i
    }.
\end{equation}
%
(This is equivalent to an expression given in \citealt{Grover:2013}.) The information matrix elements that relate to the intrinsic parameters can also be expressed as linear combinations of the angular frequency moments. However, as we will see in the next section, we need not compute these matrix elements if we are only interested in sky localization accuracy.

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{illustration}
    \caption{\label{fig:adaptive-illustration}Illustration of the \ac{BAYESTAR} adaptive mesh refinement scheme.}
\end{figure*}

@@

@@

Our sampling of the sky is relies completely on the \acl{HEALPix} (\acs{HEALPix}), a special data structure designed for all\nobreakdashes-sky maps. \ac{HEALPix} divides the sky into equal\nobreakdashes-area pixels. There is a hierarchy of \ac{HEALPix} resolutions. A \ac{HEALPix} resolution may be designated by its order $N$. The $N=0$th order or base tiling has 12 pixels. At every successive order, each tile is subdivided into four new tiles. A resolution may also be referred to by the number of subdivisions along each side of the base tiles, $N_\mathrm{side} = 2^N$. There are $N^\mathrm{pix} = 12 {N_\mathrm{side}}^2$ pixels at any given resolution. The \ac{HEALPix} projection uniquely specifies the coordinates of the center of each pixel by providing a mapping from the resolution and pixel index $(N_\mathrm{side}, i_\mathrm{pix})$ to right ascension and declination $(\alpha, \delta)$.

@@

Since \ac{BAYESTAR} is designed as one of the final steps in the real\nobreakdashes-time \ac{BNS} search, it is important to characterize how long it takes to calculate a sky map. We compiled \ac{BAYESTAR} with the Intel~C~Compiler~(\texttt{icc}) at the highest architecture\nobreakdashes-specific optimization setting (\texttt{-xhost}). We timed it under Scientific~Linux~6 on a Supermicro~1027GR\nobreakdashes-TRFT system with dual Intel Xeon E5-2670 CPUs clocked at 2.60GHz, providing a total of 16 cores and capable of executing 32 threads simultaneously (with hyperthreading). In Figure~\ref{fig:runtimes}, we show how long it took to calculate a localization with \ac{BAYESTAR} as the number of OpenMP threads was varied from 1 to 32. This is a violin plot, a smoothed vertical histogram. The red surface shows run times for a two\nobreakdashes-detector network (HL) modeled on the first scheduled Advanced \ac{LIGO} observing run in 2015, and the blue surface shows run times for a three\nobreakdashes-detector network (HLV) based on the second planned observing run in 2016. These are the two observing scenarios that will be discussed at length in the following chapter.

@@

\section{Interpretation of phase and time errors}

We take a brief digression to discuss the physical interpretation of the time and amplitude errors. For our likelihood, the \ac{CRLB} implies that
%
\begin{equation}\label{eq:covariance-matrix}
    \cov{
        \left(
        \begin{array}{c}
            \tilde{\rho}_i \\
            \tilde{\gamma}_i \\
            \tilde{\tau}_i
        \end{array}
        \right)
    } \geq \mathcal{I}^{-1} = \left(
        \begin{array}{ccc}
            1 & 0 & 0 \\
            0 & {\rho_i}^2 {\overline{\omega^2}}_i/{\omega_{\mathrm{rms},i}}^2 & {\rho_i}^2 {\overline{\omega}}_i/{\omega_{\mathrm{rms},i}}^2 \\
            0 & {\rho_i}^2 {\overline{\omega}}_i/{\omega_{\mathrm{rms},i}}^2 & {\rho_i}^2/{\omega_{\mathrm{rms},i}}^2
        \end{array}
    \right),
\end{equation}
%
where ${\omega_{\mathrm{rms},i}}^2 = {\overline{\omega^2}}_i - {{\overline{\omega}}_i}^2$. Reading off the $\tau \tau$ element of the covariance matrix reproduces the timing accuracy in Equation~(24) of \cite{FairhurstTriangulation},
%
\begin{equation}\label{eq:timing-crlb}
    \std \left(\hat{\tau}_i - \tau_i \right) \geq \sqrt{\left(\mathcal{I}^{-1}\right)_{\tau\tau}} = \frac{\rho_i}{\omega_{\mathrm{rms},i}}.
\end{equation}

@@

\section{Position resolution}

@@

How do we extract the dimensions of the localization from the Fisher matrix? If there are $N \leq 2$ detectors, then the Fisher matrix must be degenerate, because there are $3N$ measurements and 7 parameters:
%
\begin{equation*}
    \left\{
    \begin{array}{c}
        \delta\theta \\
        \delta\phi \\
        \Re[h_+] \\
        \Im[h_+] \\
        \Re[h_\times] \\
        \Im[h_\times] \\
        t_\oplus
    \end{array}
    \right\}
    = 7 \text{ parameters}
    \qquad
    \longleftrightarrow
    \qquad
    \left\{
    \begin{array}{c}
        \Re[z_i] \\
        \Im[z_i] \\
        \tau_i
    \end{array}
    \right\}
    \times N = 3N \text{ observables.}
\end{equation*}
%
Therefore, for $N=2$ detectors, the marginalized Fisher matrix $\mathcal{I}_\mathrm{marg}$ is singular. Its only nonzero eigenvalue $\lambda$ describes the width of an annulus on the sky. The width of the annulus that contains probability $p$ is given by
%
\begin{equation}\label{eq:l-pth-quantile}
    L_p = 2 \sqrt{2} \erf^{-1}(p) / \sqrt{\lambda}.
\end{equation}
%
The prefactor $2 \sqrt{2} / \erf^{-1}(p)$ is the central interval of a normal distribution that contains a probability $p$, and is $\approx 3.3$ for $p = 0.9$. \emph{Caution:} for two\nobreakdashes-detector networks, priors play an important role in practical parameter estimation and areas can be much smaller than one would predict from the Fisher matrix (see Chapter~\ref{chap:first2years} for more discussion).

@@

See code listing in Appendix~\ref{sec:fisher-matrix-code-listing}.

>>>>

\usepackage{listings}
\lstset{ %
    basicstyle=\footnotesize\ttfamily,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    keepspaces,
    frame=tb,
    commentstyle=\color{red},
    keywordstyle=\color{blue}
}

@@

\subsection{Uncertainty and the Fisher matrix}
\label{sec:fisher}

We can predict the uncertainty in the detection pipeline's \ac{ML} estimates using the \ac{CRLB}. The \ac{CRLB} has been widely applied in \ac{GW} data analysis to estimate parameter estimation uncertainty (for example, \cite{1996PhRvD..53.3033B,FairhurstTriangulation,2009PhRvD..79h4032A,WenLocalizationAdvancedLIGO,LIGOObservingScenarios,FairhurstLIGOIndia})\footnote{The Fisher matrix is also used in construction of \ac{CBC} matched filter banks. The common procedure is to place templates uniformly according to the determinant of the signal space metric, which is the Fisher matrix. This is equivalent to uniformly sampling the Jeffreys prior. In practice, this is done either by constructing a hexagonal lattice \citep{PhysRevD.76.102004} or sampling stochastically \citep{2009PhRvD..80j4014H,2009PhRvD..80b4009V,SBank,2010PhRvD..81b4004M,2014PhRvD..89b4003P}.}.

We will momentarily consider the likelihood for a single detector:
%
\begin{multline}\label{eq:gaussian-likelihood-spa}
    \mathcal{L}\left(Y_i; \rho_i, \gamma_i, \tau_i,
        \bm\theta_\mathrm{in}\right)
    \\
    \propto \exp \left[
        - \frac{1}{2} \int_0^\infty \frac{\left|Y_i (\omega)
            - X_i\left(\omega; \rho_i, \gamma_i, \tau_i,
                \bm\theta_\mathrm{in}\right)
        \right|^2}{S_i(\omega)} \, d\omega
    \right],
\end{multline}
%
with $X_i(\omega; \rho_i, \gamma_i, \tau_i, \bm\theta_\mathrm{in})$ given by Equation~(\ref{eq:signal-model}).

The Fisher information matrix for a measurement $y$ described by the unknown parameter vector $\bm{\theta}$ is the conditional expectation value
%
\begin{equation}\label{eq:general-fisher-matrix}
    \mathcal{I}_{jk} = \mathrm{E} \, \left[
        \left(\frac{\partial \log
            \mathcal{L}(Y_i ; \bm\theta)}
            {\partial \theta_j}\right)
        \left(\frac{\partial \log
            \mathcal{L}(Y_i ; \bm\theta)}
            {\partial \theta_k}\right)
    \middle| \bm\theta
    \right].
\end{equation}

The Fisher matrix describes how strongly the likelihood depends, on average, on the parameters. Furthermore, it provides an estimate of the mean-square error in the parameters. If $\hat{\bm\theta}$ is an unbiased estimator of $\bm\theta$, $\tilde{\bm\theta} = \hat{\bm\theta} - \bm\theta$ is the measurement error, and $\Sigma = \mathrm{E} \, [\tilde{\bm\theta}\tilde{\bm\theta}\transpose]$ is the covariance of the measurement error, then the \ac{CRLB} says that $\Sigma \geq \mathcal{I}^{-1}$, in the sense that $\left(\Sigma - \mathcal{I}^{-1}\right)$ is positive semi\nobreakdashes-definite.

Note that if $\log\mathcal{L}$ is twice differentiable in terms of $\bm\theta$, then the Fisher matrix can also be written in terms of second derivatives as
%
\begin{equation}\label{eq:general-fisher-matrix-second-derivatives}
    \mathcal{I}_{jk} = \mathrm{E} \, \left[
        -\frac{\partial^2 \log
            \mathcal{L}(Y_i ; \bm\theta)}
            {\partial \theta_j \partial \theta_k}
    \middle| \bm\theta
    \right].
\end{equation}

When (as in our assumptions) the likelihood is Gaussian, Equation~(\ref{eq:general-fisher-matrix}) simplifies to
%
\begin{equation}\label{eq:gaussian-fisher-matrix}
    \mathcal{I}_{jk} = \int_0^\infty \Re \left[
        \left(\frac{\partial X_i}{\partial \theta_j}\right)^*
        \left(\frac{\partial X_i}{\partial \theta_k}\right)
    \right] \frac{1}{S_i(\omega)} \, d\omega.
\end{equation}
%
This form is useful because it involves manipulating the signal $X_i (\omega)$ rather than the entire observation $Y (\omega)$. In terms of the $k$th \ac{SNR}-weighted moment of angular frequency,
%
\begin{equation}\label{eq:angular-frequency-moments}
    {\overline{\omega^k}}_i =
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \omega^k \, d\omega \right]
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \, d\omega \right]^{-1},
\end{equation}
%
the Fisher matrix for the signal in the $i$th detector is
%
\begin{equation}
    \label{eq:single-detector-block-fisher-matrix}
    \mathcal{I}_i = \left(
        \begin{array}{cc}
            \mathcal{I}_{\bm\theta_i,\bm\theta_i} &
            \mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}} \\
            {\mathcal{I}_{\bm\theta_i,\bm\theta_\mathrm{in}}}\transpose &
            {\rho_i}^2 \mathcal{I}_{\bm\theta_\mathrm{in},\bm\theta_\mathrm{in}}
        \end{array}
    \right).
\end{equation}
%
The top-left block describes only the extrinsic parameters, and is given by
%
\begin{equation}\label{eq:fisher-matrix}
    \mathcal{I}_{\bm\theta_i,\bm\theta_i} = \bordermatrix{
        ~ & \rho_i & \gamma_i & \tau_i \cr
        \rho_i & 1 & 0 & 0 \cr
        \gamma_i & 0 & {\rho_i}^2 & -{\rho_i}^2 {\overline{\omega}}_i \cr
        \tau_i & 0 & -{\rho_i}^2 {\overline{\omega}}_i & {\rho_i}^2 {\overline{\omega^2}}_i
    }.
\end{equation}
%
(This is equivalent to an expression given in \cite{Grover:2013}.) The bottom row and right column of Equation~(\ref{eq:single-detector-block-fisher-matrix}) describe the intrinsic parameters and how they are coupled to the extrinsic parameters. We show in Appendix~\ref{sec:independence-intrinsic-extrinsic} that we need not consider the intrinsic parameters at all if we are concerned only with sky localization.

The Fisher matrix has been much maligned within the \ac{GW} literature because the \ac{CRLB} is a good description of the parameter covariance in the limit of high \ac{SNR}, and can be abused by applying it in low-\ac{SNR} conditions, or close to the boundaries of the parameter space \cite{UseAbuseFisherMatrix}. However, we will put the \ac{CRLB} to good use to improve our qualitative understanding of the likelihood. Furthermore, the Fisher matrix in its own right---independent of its suitability to describe the parameter covariance---is a well-defined property of any likelihood function, and we will exploit it as such in Section~\ref{sec:bayestar-likelihood}.

For our likelihood, the \ac{CRLB} implies that
%
\begin{equation}\label{eq:covariance-matrix}
    \cov{
        \left(
        \begin{array}{c}
            \tilde{\rho}_i \\
            \tilde{\gamma}_i \\
            \tilde{\tau}_i
        \end{array}
        \right)
    } \geq \mathcal{I}^{-1} = \left(
        \begin{array}{ccc}
            1 & 0 & 0 \\
            0 & {\rho_i}^2 {\overline{\omega^2}}_i/{\omega_{\mathrm{rms},i}}^2 & {\rho_i}^2 {\overline{\omega}}_i/{\omega_{\mathrm{rms},i}}^2 \\
            0 & {\rho_i}^2 {\overline{\omega}}_i/{\omega_{\mathrm{rms},i}}^2 & {\rho_i}^2/{\omega_{\mathrm{rms},i}}^2
        \end{array}
    \right),
\end{equation}
%
where ${\omega_{\mathrm{rms},i}}^2 = {\overline{\omega^2}}_i - {{\overline{\omega}}_i}^2$. This structure implies that errors in \ac{SNR} are uncorrelated with errors in time and phase, and that there is a particular sum and difference of the times and phases that are measured independently (see Appendix~\ref{sec:interpretation-of-errors}).

Reading off the $\tau \tau$ element of the covariance matrix reproduces the timing accuracy in Equation~(24) of \cite{FairhurstTriangulation},
%
\begin{equation}\label{eq:timing-crlb}
    \std \left(\hat{\tau}_i - \tau_i \right) \geq \sqrt{\left(\mathcal{I}^{-1}\right)_{\tau\tau}} = \frac{\rho_i}{\omega_{\mathrm{rms},i}}.
\end{equation}
%
\citet{FairhurstTriangulation} goes on to frame the characteristic position reconstruction accuracy of a \ac{GW} detector network in terms of time delay triangulation, with the above formula describing the time of arrival uncertainty for each detector. In Appendix~\ref{sec:position-resolution}, we show how to extend this formalism to include the phases and amplitudes on arrival as well.

@@

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{importance-sampling}
    \caption{\label{fig:importance-sampling}Illustration of importance sampling scheme. The top-left panel shows the original integrand $f(r)$, the proposal integrand $g(r)$, and the limits of integration $r = r_\mathrm{min}$ and $r = r_\mathrm{max}$. The area of the dark shaded region is the integral of interest. The bottom-left panel shows the integral $\mathscr{G}(r) = \int_0^r g(r) dr$. The new variable of integration is $G = \mathscr{G}(r)$, from $G_\mathrm{min} = \mathscr{G}(r_\mathrm{min})$ to $G_\mathrm{max} = \mathscr{G}(r_\mathrm{max})$. The bottom-right panel shows the transformed integrand, $f(\mathscr{G}^{-1}(G))/g(\mathscr{G}^{-1}(G))$. The dark shaded region has the same area as in the top-left figure.}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{illustration}
    \caption{\label{fig:adaptive-illustration}Illustration of the \ac{BAYESTAR} adaptive HEALPix sampling scheme.}
\end{figure*}

Our sampling of the sky relies completely on the \acl{HEALPix} (\acs{HEALPix}), a special data structure designed for all\nobreakdashes-sky maps. \ac{HEALPix} divides the sky into equal\nobreakdashes-area pixels. There is a hierarchy of \ac{HEALPix} resolutions. A \ac{HEALPix} resolution may be designated by its order $N$. The $N=0$th order or base tiling has 12 pixels. At every successive order, each tile is subdivided into four new tiles. A resolution may also be referred to by the number of subdivisions along each side of the base tiles, $N_\mathrm{side} = 2^N$. There are $N^\mathrm{pix} = 12 {N_\mathrm{side}}^2$ pixels at any given resolution. The \ac{HEALPix} projection uniquely specifies the coordinates of the center of each pixel by providing a mapping from the resolution and pixel index $(N_\mathrm{side}, i_\mathrm{pix})$ to right ascension and declination $(\alpha, \delta)$.

@@

Since \ac{BAYESTAR} is designed as one of the final steps in the real\nobreakdashes-time \ac{BNS} search, it is important to characterize how long it takes to calculate a sky map. We compiled \ac{BAYESTAR} with the Intel~C~Compiler~(\texttt{icc}) at the highest architecture\nobreakdashes-specific optimization setting (\texttt{-xhost}). We timed it under Scientific~Linux~6 on a Supermicro~1027GR\nobreakdashes-TRFT system with dual Intel Xeon E5-2670 CPUs clocked at 2.60GHz, providing a total of 16 cores and capable of executing 32 threads simultaneously (with hyperthreading). In Figure~\ref{fig:runtimes}, we show how long it took to calculate a localization with \ac{BAYESTAR} as the number of OpenMP threads was varied from 1 to 32. This is a violin plot, a smoothed vertical histogram. The red surface shows run times for a two\nobreakdashes-detector network (HL) modeled on the first scheduled Advanced \ac{LIGO} observing run in 2015, and the blue surface shows run times for a three\nobreakdashes-detector network (HLV) based on the second planned observing run in 2016. These are the two observing scenarios that are discussed in \cite{FirstTwoYears}.

@@

\section{Interpretation of phase and time errors}
\label{sec:interpretation-of-errors}

@@

\section{Position resolution}
\label{sec:position-resolution}

@@

How do we extract the dimensions of the localization from the Fisher matrix? If there are $N \leq 2$ detectors, then the Fisher matrix must be degenerate, because there are $3N$ measurements and 7 parameters:
%
\begin{widetext}
\begin{equation*}
    \left\{
    \begin{array}{c}
        \delta\theta \\
        \delta\phi \\
        \Re[h_+] \\
        \Im[h_+] \\
        \Re[h_\times] \\
        \Im[h_\times] \\
        t_\oplus
    \end{array}
    \right\}
    = 7 \text{ parameters}
    \qquad
    \longleftrightarrow
    \qquad
    \left\{
    \begin{array}{c}
        \Re[z_i] \\
        \Im[z_i] \\
        \tau_i
    \end{array}
    \right\}
    \times N = 3N \text{ observables.}
\end{equation*}
\end{widetext}
%
Therefore, for $N=2$ detectors, the marginalized Fisher matrix $\mathcal{I}_\mathrm{marg}$ is singular. Its only nonzero eigenvalue $\lambda$ describes the width of an annulus on the sky. The width of the annulus that contains probability $p$ is given by
%
\begin{equation}\label{eq:l-pth-quantile}
    L_p = 2 \sqrt{2} \erf^{-1}(p) / \sqrt{\lambda}.
\end{equation}
%
The prefactor $2 \sqrt{2} / \erf^{-1}(p)$ is the central interval of a normal distribution that contains a probability $p$, and is $\approx 3.3$ for $p = 0.9$. \emph{Caution:} for two\nobreakdashes-detector networks, priors play an important role in practical parameter estimation and areas can be much smaller than one would predict from the Fisher matrix.

@@

See code listing in Appendix~A.6 of \cite{leo-singer-thesis}.
